### 2017-06-30 paper.tex
Creating home page version of paper

Decades of pedagogical research has yielded many insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
many college and university faculty have little or no training in education \cite{browning2012},
so this knowledge is rarely applied in the classroom.

@@

\bibitem{browning2012}
Brownell S.~E. and Tanner K.~D.:
Barriers to faculty pedagogical change: Lack of training, time, incentives, and...tensions with professional identity?
\newblock CBE Life Sciences Education,
\newblock 11(4), 2012,
\newblock 10.1187/cbe.12-09-0163.

>>>>

Decades of pedagogical research has yielded many insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
many college and university faculty have little or no training in education \cite{brownell},
so this knowledge is rarely applied in the classroom.

@@

\bibitem{brownell}
Brownell S.~E. and Tanner K.~D.:
Barriers to faculty pedagogical change: Lack of training, time, incentives, and...tensions with professional identity?
\newblock CBE Life Sciences Education,
\newblock 11(4), 2012,
\newblock 10.1187/cbe.12-09-0163.
